GNSS-based displacement detection using Bayesian inference for deformation monitoring

### 2020-11-23 paper/manuscript-iot.tex
proof reading 2

	\author{Nan Shen, Liang Chen\textsuperscript{*}, and Ruizhi Chen% <-this % stops a space
		\thanks{This research was funded by the National Key Research and Development Program (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No. 2018CFA007, and the Zhejiang Lab’s International Talent Fund for Young Professionals.}% <-this % stops a space
	}

@@

	% As a general rule, do not put math, special symbols or citations
	% in the abstract or keywords.
	\begin{abstract}
For decades, deformation monitoring base on the global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
With the development of Internet of Things (IOT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning in a short time.
Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
Results from simulation experiments and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding additional prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
	\end{abstract}

@@

	\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\label{intro}
	%全球定位系统系统的应用-》位移探测
	%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
	%传统测量仪器的弊端，GNSS位移探测的优势。
	%GNSS在位移探测中扮演的角色，以及位移探测的要求
	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
	\IEEEPARstart{I}{n}  recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\cite{teunissen2017springer}. 
	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to natural disaster monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields. 
	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
	With the improvement of the Internet of things (IOT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time.
	%Displacement detection involves displacement identification and extraction. 
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results. 
	There are many researches on displacement detection based on GNSS, which can be divided into two categories.

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection using PPP has been studied. There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	This kind of method mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

	In another category of GNSS-based displacement detection research, GNSS is only used as a long-term monitoring method.
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data are used as a comparison. The results showed that the accuracy of Global positioning system (GPS) measurement was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement is obtained by the direct difference between the coordinates of the start and end periods.
	In addition, GNSS is also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements are used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
	In these studies, the GNSS static positioning mode is usually adopted.

@@

	%引入本文的研究内容和贡献
	The primary aim of this paper is to explore using the context data of change point from GNSS kinematic positioning for displacement detection. This study utilized Bayesian inference to identify and extract displacement, and the Markov Chain Monte Carlo (MCMC) technique is adopted to implement the Bayesian inference. Simulation experiments and field experiments were carried out to verify the feasibility of the proposed method. The posterior sample distribution of parameters is used to analyze the reliability of displacement detection. The study presented here is one of the first investigations to utilize Bayesian inference for displacement detection based on GNSS kinematic positioning. The remaining part is as follows. Section \ref{method} shows the methodology used for this study, Section \ref{exp} presents the experimental results, the discussion is given in Section \ref{disc}, and finally, the conclusion is given in the last section.

@@

The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$,  and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of coordinate. The displacement occurrence time is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.  
The time corresponding to the $n$ change points satisfies the following relationship:$ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
The problem of displacement detection is to find out the time of displacement and estimate the displacement effectively.

\subsubsection{Bayesian Inference}
Bayesian inference is one of the most important skills in statistics. Bayesian inference deduces the posterior probability as the result of a priori probability and likelihood function. Bayesian inference calculates the posterior probability according to the Bayesian theorem\cite{chen2009modulation,chen2013bayesian}

\begin{equation}\label{eq_bayesian_inference}
P({\bf{\theta }}\left| {\bf{x}} \right.) = \frac{{P({\bf{\theta }})P({\bf{x}}\left| {\bf{\theta }} \right.)}}{{P({\bf{x}})}}
\end{equation}
where $\bf{\theta }$ is the parameter to be estimated and $\bf{x}$ is the observation;$P({\bf{\theta }}\left| {\bf{x}} \right.)$ denotes the posterior probability; $P({\bf{\theta }})$ represents a priori probability, which refers to the probability obtained from previous experience and analysis;
$P({\bf{x}}\left| {\bf{\theta }} \right.)$ is the likelihood function, which represents the probability of $x$ when a priori is established. ${P({\bf{x}})}$ is the total likelihood, which is a constant value.

\subsubsection{Likelihood Function}
It is assumed that the displacement obtained by GNSS obeys Gaussian normal distribution. The displacement of each segment segmented by the change point obeys the Gaussian distribution of different mean and same variance, which is expressed as follows

\begin{equation}\label{eq_ts_cps}
x \sim \left\{ {\begin{array}{*{20}{r}}
	{N({\mu _0},\sigma ),}&{t < {\tau _1}}\\
	{N({\mu _1},\sigma ),}&{{\tau _1} \le t < {\tau _2}}\\
	\vdots &{}\\
	{\begin{array}{*{20}{c}}
		{N({\mu _n},\sigma ),}
		\end{array}}&{{\tau _{n - 1}} \le t < {\tau _n}}\\
	{N({\mu _{n + 1}},\sigma ),}&{{\tau _n} \le t}
	\end{array}} \right.
\end{equation}
where the $n$ change points divide the time series into $n+1$ segments, and the mean values of each segment are ${\mu _0},{\mu _1},\cdots,{\mu _n}$; $\sigma$ is the standard deviation of each normal distribution; Then the likelihood probability is expressed as follows

@@

\subsubsection{Prior Distribution}
Assuming that the parameters ${\bf{\tau }}=(\tau_1,\mu_2,\cdots,\tau_n)$, ${\bf{\mu }}=(\mu_0,\mu_1,\cdots,\mu_n)$ and $\sigma$ are independent of each other, then:

\begin{equation}\label{eq_bayesian_prior}
P({\bf{\theta }}) = P({\bf{\tau }},{\bf{\mu }},\sigma ) = P({\bf{\tau }})P({\bf{\mu }})P(\sigma )
\end{equation}
The posterior distribution consists of three parts, including the prior distribution of change point, mean value and standard deviation. It is assumed that the standard deviation $\sigma$ obeys the Gaussian normal distribution and is expressed as follows

@@

\begin{equation}\label{eq_bayesian_prior_mu}
{\mu _i} \sim U({x_l },{x_u })(i = 0,1, \cdots ,n)
\end{equation}
where $x_l$ and $x_u$ represent the lower limit and  upper limit of the uniform distribution, which are determined by the mean value of the coordinate time series and the possible range of variation. Assuming that the mean values of each segment are independent of each other, then

@@

\subsubsection{Markov Chain Monte Carlo (MCMC)}
The posterior distribution of the parameters depends on the prior distribution and the likelihood function. Obtaining the posterior probability of parameters by direct integration or sum requires a lot of operations, which is difficult to achieve. In this work, the Markov chain Monte Carlo technique is used to approximate the integral or sum value. Monte Carlo sampling is to construct the integral or sum function as the expectation under a certain distribution, and then approximate the expectation by the corresponding average value\cite{goodfellow2016deep}.

\begin{equation}\label{eq_monte_carlo_1}
s =\sum\limits_x g(x)= \sum\limits_x {p(x)f(x) = {E_p}[f(x)]}
\end{equation}
\begin{equation}\label{eq_monte_carlo_2}
s =\int {g(x)}= \int {p(x)f(x)dx}  = {E_p}[f(x)]
\end{equation}
where $g(x)$ is the function to be integrated or summated; $p(x)$ is the probability distribution or probability density function of $x$. The integral or summation problem of $g(x)$ is transformed into the mathematical expectation problem of $f(x)$ under the distribution $p(x)$. This mathematical expectation can be approximated by sampling from $p(x)$.

\begin{equation}\label{eq_monte_carlo_3}
\hat s = \frac{1}{n}\sum\limits_{i = 1}^n {f({x_i})}
\end{equation}
where $x_i$ is the sample with the distribution of $p(x)$. As can be seen from the above, Monte Carlo method as a general sampling simulation sum or integration method, depends on sampling from the distribution of $p(x)$. However, it is not easy to directly sample from the target distribution of $p(x)$. At present, the most popular solution is to use Markov chain Monte Carlo sampling, which provides a general way to construct a sequence that converges to the target distribution. According to Markov chain, the probability of state transition at a certain time only depends on its previous state, which is expressed as follows

\begin{equation}\label{eq_markov_chain_1}
P({x_{n + 1}}\left| {{x_n},{x_{n - 1}}} \right.,{x_{n - 2}}, \cdots ,{x_2},{x_1}) = P({x_{n + 1}}\left| {{x_n}} \right.)
\end{equation}
If a Markov process is neither periodic nor irreducible, then the Markov process is ergodic, that is, each state appears with a certain probability. The Markov process of ergodic states has an important property: no matter what the initial state probability is, the Markov process of the ergodic state tends to be a stable distribution after enough state transitions.
That is, for the initial probability distribution is $\pi_0(x)$, the probability distribution after several rounds of state transition is as follows

@@

\begin{equation}\label{eq_markov_chain_3}
\pi_{n}(x)=\pi_{n+1}(x)=\pi_{n+2}(x)\cdots
\end{equation}
This is the target distribution we want to construct. Based on the initial arbitrary simple probability distribution such as Gaussian distribution $\pi_{0}(x)$, the state value $x_0$ is obtained by sampling. Based on the probability distribution $\pi_{1}(x)=\pi_{0}(x)P(x\left| {{x_0}} \right.)$ sampling state value $x_1$, using the same method, execute $n$ times. Sample $(x_{n},x_{n+1},x_{n+2}\cdots)$ is the corresponding sample set of the target distribution. However, the implementation of MCMC also needs to consider other factors such as constructing the state transition matrix according to the target distribution, which is beyond the scope of this work. Two implementations of MCMC,  the Metropolis-Hasting sampler\cite{chib1995understanding} and the No-U-Turn sampler\cite{hoffman2014no}, are used to sample discrete random variables and continuous random variables, respectively. Next, the data source of the proposed method: GNSS real-time kinematic positioning is introduced.

>>>>

	\author{Nan Shen, Liang Chen\textsuperscript{*}, and Ruizhi Chen% <-this % stops a space
		\thanks{This research was funded by the National Key Research and Development Program (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No. 2018CFA007.}% <-this % stops a space
	}

@@

	% As a general rule, do not put math, special symbols or citations
	% in the abstract or keywords.
	\begin{abstract}
For decades, deformation monitoring based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
With the development of Internet of Things (IOT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning in a short time.
Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
	\end{abstract}

@@

	\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\label{intro}
	%全球定位系统系统的应用-》位移探测
	%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
	%传统测量仪器的弊端，GNSS位移探测的优势。
	%GNSS在位移探测中扮演的角色，以及位移探测的要求
	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
	\IEEEPARstart{I}{n}  recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\cite{teunissen2017springer}. 
	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to natural landslide monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields. 
	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
	With the improvement of the Internet of things (IOT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time.
	%Displacement detection involves displacement identification and extraction. 
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}. 
	There are many researches on displacement detection based on GNSS, which can be divided into two categories.

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}. The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using PPP has been studied. The results showed that PPP can be capable of detecting large landslides.
	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

	In another category of GNSS-based displacement detection research, GNSS is only used as a static positioning method.
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data are used as a comparison. 
	The results showed that the accuracy of the Global positioning system (GPS) measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	In addition, GNSS was also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements were used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
	In these studies, the GNSS static positioning mode is usually adopted.

@@

	%引入本文的研究内容和贡献
	The primary aim of this paper is to explore using the context data of change point from GNSS kinematic positioning for displacement detection. 
	This study utilized Bayesian inference to identify and extract displacement, and the Markov Chain Monte Carlo (MCMC) technique is adopted to implement the Bayesian inference. 
	Simulation and field experiments were carried out to verify the feasibility of the proposed method. 
	The posterior sample distribution of parameters is used to analyze the reliability of displacement detection. 
	The study presented here is one of the first investigations to utilize Bayesian inference for displacement detection based on GNSS kinematic positioning. 
	The remaining part is as follows. Section \ref{method} shows the methodology used for this study, Section \ref{exp} presents the experimental results, the discussion is given in Section \ref{disc}, and finally, the conclusion is given in the last section.

@@

The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$, and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of coordinate. The displacement occurrence time is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.  
The time corresponding to the $n$ change points satisfies the following relationship:$ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
The problem of displacement detection is to find out the time of displacement and estimate the displacement.

\subsubsection{Bayesian Inference}
Bayesian inference is one of the most important skills in statistics, and deduces the posterior probability as the result of a priori probability and likelihood function\cite{robert2014machine}. Bayesian inference calculates the posterior probability according to the Bayesian theorem\cite{chen2009modulation,chen2013bayesian}

\begin{equation}\label{eq_bayesian_inference}
P({\bf{\theta }}\left| {\bf{x}} \right.) = \frac{{P({\bf{\theta }})P({\bf{x}}\left| {\bf{\theta }} \right.)}}{{P({\bf{x}})}}
\end{equation}
where $\bf{\theta }$ is the parameter to be estimated and $\bf{x}$ is the observation; $P({\bf{\theta }}\left| {\bf{x}} \right.)$ denotes the posterior probability; $P({\bf{\theta }})$ represents a priori probability, which refers to the probability obtained from previous experience and analysis;
$P({\bf{x}}\left| {\bf{\theta }} \right.)$ is the likelihood function, which represents the probability of $x$ when a priori is established. ${P({\bf{x}})}$ is the total likelihood, which is a constant value.

\subsubsection{Likelihood Function}
It is assumed that the displacement obtained by GNSS kinematic positioning obeys Gaussian normal distribution.  The displacement of each segment segmented by the change points obeys the Gaussian distribution of different mean and same variance, which is expressed as follows

\begin{equation}\label{eq_ts_cps}
x \sim \left\{ {\begin{array}{*{20}{r}}
	{N({\mu _0},\sigma ),}&{t < {\tau _1}}\\
	{N({\mu _1},\sigma ),}&{{\tau _1} \le t < {\tau _2}}\\
	\vdots &{}\\
	{\begin{array}{*{20}{c}}
		{N({\mu _{n-1}},\sigma ),}
		\end{array}}&{{\tau _{n - 1}} \le t < {\tau _n}}\\
	{N({\mu _{n}},\sigma ),}&{{\tau _n} \le t}
	\end{array}} \right.
\end{equation}
where the $n$ change points divide the time series into $n+1$ segments, and the mean values of each segment are ${\mu _0},{\mu _1},\cdots,{\mu _n}$; $\sigma$ is the standard deviation of each normal distribution; Then the likelihood probability is expressed as follows

@@

\subsubsection{Prior Distribution}
Assuming that the parameters ${\bf{\tau }}=(\tau_1,\tau_2,\cdots,\tau_n)$, ${\bf{\mu }}=(\mu_0,\mu_1,\cdots,\mu_n)$ and $\sigma$ are independent of each other, then:

\begin{equation}\label{eq_bayesian_prior}
P({\bf{\theta }}) = P({\bf{\tau }},{\bf{\mu }},\sigma ) = P({\bf{\tau }})P({\bf{\mu }})P(\sigma )
\end{equation}
The prior distribution consists of three parts, including the prior distribution of change point, mean value and standard deviation. It is assumed that the standard deviation $\sigma$ obeys the Gaussian normal distribution and is expressed as follows

@@

\begin{equation}\label{eq_bayesian_prior_mu}
{\mu _i} \sim U({\mu_l },{\mu_u })(i = 0,1, \cdots ,n)
\end{equation}
where $\mu_l$ and $\mu_u$ represent the lower limit and  upper limit of the uniform distribution, which are determined by the mean value of the coordinate time series and the possible range of variation. Assuming that the mean values of each segment are independent of each other, then

@@

\subsubsection{Markov Chain Monte Carlo (MCMC)}
The posterior distribution of the parameters depends on the prior distribution and the likelihood function. Obtaining the posterior probability of parameters by direct integration or sum requires a lot of operations, which is difficult to achieve\cite{robert2013monte}. In this work, the Markov chain Monte Carlo technique is used to approximate the integral or sum value. Monte Carlo sampling is to construct the integral or sum function as the expectation under a certain distribution, and then approximate the expectation by the corresponding average value\cite{goodfellow2016deep}.

\begin{equation}\label{eq_monte_carlo_1}
s =\sum\limits_x g(x)= \sum\limits_x {p(x)f(x) = {E_p}[f(x)]}
\end{equation}
\begin{equation}\label{eq_monte_carlo_2}
s =\int {g(x)}= \int {p(x)f(x)dx}  = {E_p}[f(x)]
\end{equation}
where $g(x)$ is the function to be integrated or summated; $p(x)$ is the probability distribution or probability density function of $x$. The integral or summation problem of $g(x)$ is transformed into the mathematical expectation problem of $f(x)$ under the distribution $p(x)$. This mathematical expectation can be approximated by sampling from $p(x)$\cite{goodfellow2016deep}.

\begin{equation}\label{eq_monte_carlo_3}
\hat s = \frac{1}{n}\sum\limits_{i = 1}^n {f({x_i})}
\end{equation}
where $x_i$ is the sample with the distribution of $p(x)$. As can be seen from the above, Monte Carlo method as a general sampling simulation sum or integration method, depends on sampling from the distribution of $p(x)$. However, it is not easy to directly sample from the target distribution of $p(x)$. At present, the most popular solution is to use Markov chain Monte Carlo sampling, which provides a general way to construct a sequence that converges to the target distribution. According to Markov chain, the probability of state transition at a certain time only depends on its previous state, which is expressed as follows\cite{robert2013monte}

\begin{equation}\label{eq_markov_chain_1}
P({x_{n + 1}}\left| {{x_n},{x_{n - 1}}} \right.,{x_{n - 2}}, \cdots ,{x_2},{x_1}) = P({x_{n + 1}}\left| {{x_n}} \right.)
\end{equation}
If a Markov process is neither periodic nor irreducible, then the Markov process is ergodic, that is, each state appears with a certain probability. The Markov process of ergodic states has an important property: no matter what the initial state probability is, the Markov process of the ergodic state tends to be a stable distribution after enough state transitions\cite{robert2013monte}.
That is, for the initial probability distribution is $\pi_0(x)$, the probability distribution after several rounds of state transition is as follows

@@

\begin{equation}\label{eq_markov_chain_3}
\pi_{n}(x)=\pi_{n+1}(x)=\pi_{n+2}(x)\cdots
\end{equation}
This is the target distribution we want to construct. Based on the initial arbitrary simple probability distribution such as Gaussian distribution $\pi_{0}(x)$, the state value $x_0$ is obtained by sampling. Based on the probability distribution $\pi_{1}(x)=\pi_{0}(x)P(x\left| {{x_0}} \right.)$ sampling state value $x_1$, using the same method, execute $n$ times. Sample $(x_{n},x_{n+1},x_{n+2}\cdots)$ is the corresponding sample set of the target distribution. However, the implementation of MCMC also needs to consider other factors such as constructing the state transition matrix according to the target distribution\cite{robert2013monte}, which is beyond the scope of this work. Two implementations of MCMC,  the Metropolis-Hasting sampler\cite{chib1995understanding} and the No-U-Turn sampler\cite{hoffman2014no}, are used to sample discrete random variables and continuous random variables, respectively. Next, the data source of the proposed method: GNSS real-time kinematic positioning is introduced.

\subsection{Relative real-time kinematic (RTK)}
There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
Kalman filter is used in the implementation of  RTK, and the observation model, the state model, and the extended Kalman filtering process of RTK are introduced below. 
\subsubsection{Observation model}
The double-difference(DD) observation model is usually used in RTK, and its definition is shown in (\ref{eq_dd_obs})\cite{teunissen2017springer}.
\begin{figure*}
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla \delta I_{\Phi {i_{br}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
	\end{array} \right\}
	\label{eq_dd_obs}
	\end{equation}
\end{figure*}
In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $j$ and $k$ represent the satellites;
$\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; 
$\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; 
$\Delta \nabla \delta M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \delta M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; 
$\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD measurement noise of pseudo-range and carrier-phase, respectively; 
$\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations\cite{teunissen2017springer}; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites. 
For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
\begin{figure*}
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
	\label{eq_dd_obs_simplified}
	\end{equation}
